Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
fix minor spelling error

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races). Thanks to partnerships with state education authorities and organisations, NCES is authorised to collected data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024]. Its National Forum on Education Statistics then collects, processes and reports elementary and local education statistics [@Encyclopedia_2024].

@@

This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA]. Data are obtained from the Departments of Education for the 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY). Each state collects data from constituent schools, school boards and school authorities [@DeptsEd]. The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022. Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.

>>>>

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district and for each of the years 2018, 2019 and 2020, it reports the total student enrollment, split by grade (ranging from Kindergarten to Grade 12), sex (Male and Female), and ethnic class (American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races). Thanks to partnerships with state education authorities and organisations, NCES is authorised to collect such data by conducting numerous surveys with public schools and local education agencies [@Encyclopedia_2024]. Its National Forum on Education Statistics then collects, processes and reports elementary and local education statistics [@Encyclopedia_2024].

@@

This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA]. Data are obtained from the Departments of Education for the 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY). Each state collects data via surveys from constituent schools, school boards and school authorities [@DeptsEd]. The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022. Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.
